Model Adaptivity for Goal-Oriented Inference using Adjoints

### 2016-11-23 paper/intro_v3.tex
ahhh mixed up some versions last commit

Physical and engineering systems are often described using sophisticated mathematical models, such as coupled, nonlinear partial differential equations (PDEs). On the other hand, the inverse problem seeks to infer unknown model parameters using observed data; often these observations are limited, noisy and provide only indirect information about the unknown parameters. Many such inverse problems present a major computational challenge, since their solution involves repeated solutions of complex mathematical models. In many cases, a given physical system can be represented with varying degrees of fidelity by different models. A higher-fidelity model more accurately represents reality, but is also usually more computationally expensive to solve. Lower-fidelity models can solved inexpensively, at the expense of introducing model errors. In this work, we formulate an approach for leveraging multiple models of varying fidelities in the solution of an inverse problem.

>>>>

Physical and engineering systems are often described using sophisticated mathematical models, such as coupled, nonlinear partial differential equations (PDEs). The inverse problem seeks to infer unknown model parameters using observed data; often these observations are limited, noisy and provide only indirect information about the unknown parameters. Many such inverse problems present a major computational challenge, since their solution involves repeated solutions of the mathematical model. In many cases, a given physical system can be represented with varying degrees of fidelity by different models. A higher-fidelity model more accurately represents reality, but is also usually more computationally expensive to solve. Lower-fidelity models can be solved inexpensively, at the expense of introducing approximations. In this work, we formulate an approach for leveraging multiple models of varying fidelities in solution of an inverse problem.
